A supertree pipeline for summarizing phylogenetic and taxonomic information for millions of species

### 2017-01-26 doc/paper1-submission/paper5-adjusted.tex
Make references to panels more explicit.

\caption{Input trees and taxonomy tree}
\label{fig:cleaned-phylo-example}
\end{figure}

@@

\caption{Exemplified input trees and taxonomy tree from Fig. \ref{fig:cleaned-phylo-example}.
E in tree1 is exemplified by E1. Pruned taxa are E2, F2, and D. The
taxa E and F are retained as monotypic taxa in the pruned taxonomy
$\protect\prunedTaxonomy$, but are not shown in panel c. The red
edge in the pruned taxonomy tree is an uncontested higher taxon in
the exemplified taxonomy (as explained in section \ref{subsec:Subproblem-decomposition})}
\label{fig:exemplify-example}
\end{figure}

@@

\caption{Subproblems generated from the exemplified trees shown in Fig. \ref{fig:exemplify-example}.
A trivial statement from the first tree that a taxon labelled $ABCD$
is sister to $E$ has been omitted, because trees with only 2 leaves
do not contain phylogenetic information.
Similarly, the trivial problems that list E1 and F1 as the only daughters
of taxa E and F have been omitted.}
\label{fig:subproblems-example}
\end{figure}
\begin{figure}
\subfloat[]{\includegraphics[scale=0.57]{Fig7a}

@@

\caption{Solutions to the subproblems depicted in Fig. \ref{fig:subproblems-example}}
\label{fig:subproblem-solutions.}
\end{figure}

>>>>

\caption{Input trees (a-b) and taxonomy tree (c).}
\label{fig:cleaned-phylo-example}
\end{figure}

@@

\caption{Exemplified input trees (a-b) and taxonomy tree (c) from Fig. \ref{fig:cleaned-phylo-example}.
Taxon E in (a) is exemplified by E1. Pruned taxa are E2, F2, and D. The
taxa E and F are retained as monotypic taxa in the pruned taxonomy
$\protect\prunedTaxonomy$, but are not shown in panel (c). The red
edge in the pruned taxonomy tree is an uncontested higher taxon in
the exemplified taxonomy (as explained in section \ref{subsec:Subproblem-decomposition})}
\label{fig:exemplify-example}
\end{figure}

@@

\caption{Subproblems \emph{ABCD} and \emph{root} generated from the exemplified trees shown in Fig. \ref{fig:exemplify-example}.
A trivial statement from the first tree that a taxon labelled $ABCD$
is sister to $E$ has been omitted, because trees with only 2 leaves
do not contain phylogenetic information.
Similarly, the trivial problems that list E1 and F1 as the only daughters
of taxa E and F have been omitted.}
\label{fig:subproblems-example}
\end{figure}
\begin{figure}
\subfloat[]{\includegraphics[scale=0.57]{Fig7a}

@@

\caption{Solutions to subproblem \emph{ABCD} and subproblem \emph{root} depicted in Fig. \ref{fig:subproblems-example}.}
\label{fig:subproblem-solutions.}
\end{figure}
